SKIN LESION CLASSIFICATION ON IMBALANCED DATA USING DEEP LEARNING WITH SOFT ATTENTION

### 2022-09-11 MDPI/sensors-1915564/template.tex
Update Paper Review 1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{makecell}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{comment}

@@

% Abstract (Do not insert blank lines, i.e. \\) s
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of SOTA model such as DenseNet, InceptionNet, ResNet, NasNet, and MobileNet and Soft-Attention is proposed. Furthermore, personal information including age and gender are also used. It is worth to note that a new loss function	that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively. Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than InceptionResNetV2.}

@@

\section{Introduction} 
\subsection{Problem Statement}
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500 \cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6 \cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase \cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States \cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent. However, once the disease progresses beyond the skin, survival is poor \cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.

@@

\subsection{Related Works}
Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in \cite{03358}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \cite{06993}, InceptionResNetV2 \cite{00567}, ResNet50 \cite{03385} \cite{05027}, VGG16 \cite{1556} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer.

Using those above backbones has been tried by many previous papers. Rishu Garg et al   \cite{03798} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set. Besides, they also use data augmentation to avoid the imbalance of the data set. Histogram Equalization is also used to increase the contrast of the skin lesions before feeding into the Machine Learning algorithms including Random Forest, XGBoost, Support Vector Machine.

Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3 \cite{00567} model. In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set. Before feeding into the Deep CNN models, the image is resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2 and (229, 229) for InceptionV3.

Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet \cite{11946} and SeNET \cite{01507} instead and CutOut \cite{04552v2} method which involves creating holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process.

Otherwise, \cite{01284} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.

Another state of the art is GradCam and Kernel SHAP \cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In that research they use three data sets containing HAM10000, BCN-20000 and MSK. Before feeding into the models, the images are preprocessed by binarized with a very low threshold to find the center of mass.

On the other hand, there are also many state of the art whose great performance on skin lesion classification. The Student and Teacher Model is also a high performance model in 2021 \cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn.

SkinLinkNet \cite{12602} and WonderM \cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450, 600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively.

Another approach is using metadata including gender, age, and capturing position as stated in  \cite{03910} by Nil Gessert et al. The metadata is fed into fully connected neural network after being encoded into one-hot vector. All missing data point of age is set to 0. To overcome the missing data problem, the research apply one-hot encoding to the group but the initial validation is poor performance then numerical encoding is applied.

On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by  \cite{03798} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in \cite{10348} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al.

\begin{table}
	\centering
	\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} |}
		\hline
		Research & Deep Learning & Machine Learning & Data 
		Augmentation & Feture Extraction & Data set\\
		\hline
		\cite{03358} & x & & x & & HAM10000\\
		\hline
		\cite{03798} & x & x & x & x & HAM10000\\
		\hline
		\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
		\hline
		\cite{09418} & x & & x & & HAM10000\\
		\hline
		\cite{01284} & x & & x & & HAM10000\\
		\hline
		\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
		\hline
		\cite{03225} & x & & x & & HAM10000\\
		\hline
		\cite{12602} & x & & x & & HAM10000\\
		\hline
		\cite{03426} & x & & x & & HAM10000\\
		\hline
		\cite{03910} & x & & x & & HAM10000\\
		\hline
		\cite{05045} & & x & x & x & HAM10000\\
		\hline
	\end{tabular}
	\caption{Related Works Summary.}
	\label{table:related-work-summary}
\end{table}
\subsection{Proposed Method}
In this research, a new model is constructed from the combination of:\\
- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
- Using metadata including age, gender, localization as another input of the model\\
- Using Soft-Attention as a feature extractor of the model\\
- A new weight loss function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Materials}
\subsubsection{Image Data}
The data set used in this paper is the HAM10000 data set published by Havard University Dataverse \cite{10417}. There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the Table \ref{table:data-distribution} below:

@@

\subsubsection{Input Schema}
In this research, the image data is both augmented for all class, the number of image increase to 18015 images and keep original form. Before feeding into the backbone model, the images is pre-processed by the input requirement of each model. DenseNet201 \cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152 \cite{03385} \cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet \cite{04861} \cite{04381} \cite{02244}, NasNetMobile and NasNetLarge \cite{07012} require the input pixel is in range of $-1$ and $1$.

@@

\subsubsection{Soft-Attention Module}
Soft-Attention has been used in various applications: image caption generation such as \cite{03044} or handwriting verification \cite{202017}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. Soft-Attention is described in below equation:
\[
f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]
The Figure \ref{fig:soft-attention} shows the two main steps of applying Soft-Attention is applied in two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map \cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network (CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the soft-max function to generate K (a constant value) attention maps. These $K$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.

@@

In this research, the Soft-Attention layer is applied in the same way in this research \cite{03358}. The Soft-Attention module is described in the figure \ref{fig:soft-attention-block}

@@

\subsubsection{Loss Function}
The loss function used in this paper is categorical cross-entropy. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and $C$ is the number of training examples and number of class respectively. The categorical cross-entropy loss is presented as:
\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$. Since the data set face the imbalanced problem then class weight for the loss is applied. In this research, both of the original weight and a new weight formula is implementation. Originally, the weight is calculated by taking the inverse of percentage that each class accounts for. The new weight formula is described as follow:
\[W = N \odot D\]
\[D = \begin{bmatrix}
	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
	\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
\end{bmatrix}\]
where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.

>>>>

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{makecell}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{soulutf8}
\usepackage[adjustmargins]{LatexPackage/trackchanges}
\addeditor{H.K.D}

@@

% Abstract (Do not insert blank lines, i.e. \\) s
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of \add[H.K.D]{one} SOTA model \change[H.K.D]{such as}{including} DenseNet, InceptionNet, ResNet, NasNet,  MobileNet and Soft-Attention is proposed. Furthermore, personal information including age and gender are also used. It is worth to note that a new loss function	that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively. Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than InceptionResNetV2.}

@@

\section{Introduction} 
\subsection{Problem Statement}
\change[H.K.D]{One of the most common malignancies that cause death globally is skin cancer. In the United States, more than 9500 persons receive a skin cancer diagnosis each day \mbox{\cite{03358}}. The Skin Cancer Foundation reports that there is an ongoing rise in the incidence of skin cancer worldwide \mbox{\cite{11872}}. In the United States, 192,310 new cases of melanoma are anticipated to be detected in 2019. On the other hand, if patients receive an early diagnosis, their chances of survival are 99 percent. Survival is, however, generally poor after the illness has spread beyond the skin \mbox{\cite{11872}}. Additionally, there is a need for an efficient solution because to the rising prevalence of skin malignancies, low awareness among a population that is expanding, and a lack of sufficient clinical competence and services.}{Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500 \mbox{\cite{03358}} people in the United States are diagnosed with skin cancer. Otherwise, 3.6 \mbox{\cite{03358}} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase \mbox{\cite{11872}}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States \mbox{\cite{11872}}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent. However, once the disease progresses beyond the skin, survival is poor \mbox{\cite{11872}}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.}

@@

\subsection{Related Works}
\change[H.K.D]{Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in \mbox{\cite{03358}}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \mbox{\cite{06993}}, InceptionResNetV2 \mbox{\cite{00567}}, ResNet50 \mbox{\cite{03385} \cite{05027}}, VGG16 \mbox{\cite{1556}} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer.

Using those above backbones has been tried by many previous papers. Rishu Garg et al \mbox{\cite{03798}} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set. Besides, they also use data augmentation to avoid the imbalance of the data set. Histogram Equalization is also used to increase the contrast of the skin lesions before feeding into the Machine Learning algorithms including Random Forest, XGBoost, Support Vector Machine.

Amirreaza et al \mbox{\cite{10348}} do not only use those above backbone model but also used InceptionV3 \mbox{\cite{00567}} model. In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set. Before feeding into the Deep CNN models, the image is resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2 and (229, 229) for InceptionV3.

Another paper that uses the backbone models is \mbox{\cite{09418}}, Hemanth et al decide to use EfficientNet \mbox{\cite{11946}} and SeNET \mbox{\cite{01507}} instead and CutOut \mbox{\cite{04552v2}} method which involves creating holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process.

Otherwise, \mbox{\cite{01284}} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.

Another state of the art is GradCam and Kernel SHAP \mbox{\cite{06612}}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In that research they use three data sets containing HAM10000, BCN-20000 and MSK. Before feeding into the models, the images are preprocessed by binarized with a very low threshold to find the center of mass.

On the other hand, there are also many state of the art whose great performance on skin lesion classification. The Student and Teacher Model is also a high performance model in 2021 \mbox{\cite{03225}}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn.

SkinLinkNet \mbox{\cite{12602}} and WonderM \mbox{\cite{03426}} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450, 600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively.

Another approach is using metadata including gender, age, and capturing position as stated in \mbox{\cite{03910}} by Nil Gessert et al. The metadata is fed into fully connected neural network after being encoded into one-hot vector. All missing data point of age is set to 0. To overcome the missing data problem, the research apply one-hot encoding to the group but the initial validation is poor performance then numerical encoding is applied.

On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by \mbox{\cite{03798}} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in \mbox{\cite{10348}} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \mbox{\cite{05045}} by Michele Alberti et al.}

{Skin lesion classification is not a new area, since there are many great performance models constructed, recent years. The skin classification approaches can be divided into two main approaches: Deep Learning and Machine Learning. Both approaches gain great performance. Data Augmentation and Feature Extractor, otherwise are two main supporters that make the model better.
	\begin{table}[H]
		\centering
		\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} |}
			\hline
			Research & Deep Learning & Machine Learning & Data 
			Augmentation & Feture Extraction & Data set\\
			\hline
			\cite{03358} & x & & x & & HAM10000\\
			\hline
			\cite{03798} & x & x & x & x & HAM10000\\
			\hline
			\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
			\hline
			\cite{09418} & x & & x & & HAM10000\\
			\hline
			\cite{01284} & x & & x & & HAM10000\\
			\hline
			\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
			\hline
			\cite{03225} & x & & x & & HAM10000\\
			\hline
			\cite{12602} & x & & x & & HAM10000\\
			\hline
			\cite{03426} & x & & x & & HAM10000\\
			\hline
			\cite{03910} & x & & x & & HAM10000\\
			\hline
			\cite{05045} & & x & x & x & HAM10000\\
			\hline
		\end{tabular}
		\caption{Related Works Summary.}
		\label{table:related-work-summary}
	\end{table}
\subsubsection{Deep Learning Approach}
In Deep Learning, one of the most cutting-edge technologies that have been used is Soft-Attention as stated in \mbox{\cite{03358}}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \mbox{\cite{06993}}, InceptionResNetV2 \mbox{\cite{00567}}, ResNet50 \mbox{\cite{03385} \cite{05027}}, VGG16 \mbox{\cite{1556}} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer. Soumyyak et al proposed method gain a greate performance and also outperform many other studies with the accuracy of 0.93 and the precision of 0.92. However using the Data Augmentation on an imbalanced data set make the model cannot classify well on all of the classes, therefore their model got the recall and f1-score of 0.71 and 0.75, respectively. In this research, our proposed method also consider this problem and solve it.

Using those above backbones has been tried by many previous papers. Rishu Garg et al \mbox{\cite{03798}} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set. Besides, they also use data augmentation to avoid the imbalance of the data set. Histogram Equalization is also used to increase the contrast of the skin lesions before feeding into the Machine Learning algorithms including Random Forest, XGBoost, Support Vector Machine.	Histogram Equalization can be consider as a heat map that takes the main feature as the number of occurrences of the same value pixel. This approach also gain great performance with the accuracy of 0.90 and the precision of 0.88. However this approach can be bias since the one skin image of the data set contain the skin lesion at the center and the background skin so that histogram may treat background with more number of occurrence of the same pixel value. In this research, our proposed method use the Soft-Attention which can create a heat map feature of the lesion. Otherwise, Rishu Garg et al proposed method also face the problem of imbalanced classifying due to the imbalanced data set with the f1-score and recall is 0.77 and 0.74, respectively.

Amirreaza et al \mbox{\cite{10348}} do not only use those above backbone model but also used InceptionV3 \mbox{\cite{00567}} model. In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set. Before feeding into the Deep CNN models, the image is resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2 and (229, 229) for InceptionV3. The best ROC AUC values for melanoma and basal
cell carcinoma are 0.94 (ResNet152) and 0.93 (DenseNet201).

Another paper that uses the backbone models is \mbox{\cite{09418}}, Hemanth et al decide to use EfficientNet \mbox{\cite{11946}} and SeNET \mbox{\cite{01507}} instead and CutOut \mbox{\cite{04552v2}} method which involves creating holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process. Although this approach get the accuracy of 0.88, it may be bias due to the CutOut method since this method can create a hole overlap the skin lesion field. The method accuracy is also low due to the data augmentation process.

Otherwise, \mbox{\cite{01284}} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost. This approach get the accuracy of 0.86. Although, this approach figure out the data imbalance problem, got a low accuracy may due to the RandArgument. If the skin lesion part of the image is quite big or quite small the cropped image may contain only skin or the lesion spread out the whole image.

Another state of the art is GradCam and Kernel SHAP \mbox{\cite{06612}}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In that research they use three data sets containing HAM10000, BCN-20000 and MSK. Before feeding into the models, the images are preprocessed by binarized with a very low threshold to find the center of mass. This approach got the AUC score of 0.85.

On the other hand, there are also many state of the art whose great performance on skin lesion classification. The Student and Teacher Model is also a high performance model in 2021 \mbox{\cite{03225}}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn. The Student and Teacher model get the accuracy of 0.85, however the precision and f1-score are quite low 0.76.

SkinLinkNet \mbox{\cite{12602}} and WonderM \mbox{\cite{03426}} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450, 600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively. This approach get the AUC score of 0.92.

Another approach is using metadata including gender, age, and capturing position as stated in \mbox{\cite{03910}} by Nil Gessert et al. The metadata is fed into fully connected neural network after being encoded into one-hot vector. All missing data point of age is set to 0. To overcome the missing data problem, the research apply one-hot encoding to the group but the initial validation is poor performance then numerical encoding is applied. The metadata is then fed into two block networks, each one containing a Dense Layer, a Batch Normalization, a ReLU activation function, and a Dropout. After all the feature vector extract from image is then concatenate with the feature vector extracted from metadata. Otherwise, the data augmentation is also applied. This approach got the recall score of 0.74. The low recall score may be due to the imbalanced data set.

\subsubsection{Machine Learning Approach}
In Machine Learning, there are also many approaches. Since the image data is quite complex for Machine Learning algorithm, therefore using feature extractor or feature preprocessing to another form of data is recommended.

Random Forest, XGBoost, and Support Vector Machines are tested by \mbox{\cite{03798}} of Rishu Garg et al. In this approach, the data is fed directly into the Machine Learning algorithm and show out no promising result, therefore Rishu Garg et al dose not show the result of the Machine Learning algorithm.

Besides, Deep Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in \mbox{\cite{09365}} by Amirreza Rezvantalab et al. In the Deep Isolation Forest, an feature extractor is applied by using CNN to learn the main pattern of the image. After that, the feature map is then fed into K isolation forest estimators using bagging algorithm. The Deep Isolation Forest got the accuracy of 0.9 and the confidence of 0.86. However, the AUC score is just 0.74, this may due to the limitation of Machine Learning algorithm.

Matrix Transformation, otherwise is also applied before the soft-max activation function in \mbox{\cite{05045}} by Michele Alberti et al. In this approach the image is fed into a general model using sequence of residual block. The feature maps created from those above residual block is then fed into an Global Average Pooling to create a feature vector. This feature vector is then extracted by CNN-1D and transformed by Discrete Fourier Transformation (DFT) as a filter before going to the soft-max layer. 
}

\subsection{Proposed Method}
In this research, a new model is constructed from the combination of:\\
- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
- Using metadata including age, gender, localization as another input of the model\\
- Using Soft-Attention as a feature extractor of the model\\
- A new weight loss function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Materials}
\subsubsection{Image Data}
The data set used in this paper is the HAM10000 data set published by Havard University Dataverse \cite{10417}. There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the Table \ref{table:data-distribution} below:

@@

\subsubsection{Input Schema}
\add[H.K.D]{Image preprocessing is an essential part before the training process because of the ability to extract main pattern of an image. In this stage, the image can be changed the color channel so that the main feature is separated from the useless part. Image Retrieval, otherwise has significantly create a vector that represent the main feature of an image. Those image retrieval techniques can be energy compaction, primitive pattern units, etc. Shervan Fekri-Ershad et al create an feature vector by calculating the element wise product of histogram vector in each channel of an image \mbox{\cite{2012.4305}}. Then comparing the Euclidean distance between this feature vector and the average feature vector of the whole data set with a thresh hold, they can extract the skin part of the image.}

In this research, the image data is both augmented for all class, the number of image increase to 18015 images and keep original form. Before feeding into the backbone model, the images is pre-processed by the input requirement of each model. DenseNet201 \cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152 \cite{03385} \cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet \cite{04861} \cite{04381} \cite{02244}, NasNetMobile and NasNetLarge \cite{07012} require the input pixel is in range of $-1$ and $1$.

@@

\subsubsection{Soft-Attention Module}
Soft-Attention has been used in various applications: image caption generation such as \cite{03044} or handwriting verification \cite{202017}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. Soft-Attention is described in the Equation \ref{eqn:softatt}.
\begin{equation}
	\label{eqn:softatt}
	f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\end{equation}

The Figure \ref{fig:soft-attention} shows the two main steps of applying Soft-Attention is applied in two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map \cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network (CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the soft-max function to generate K (a constant value) attention maps. These $K$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.

@@

In this research, the Soft-Attention layer is applied in the same way in this research \cite{03358}. The Soft-Attention module is described in the figure \ref{fig:soft-attention-block}.

@@

\subsubsection{Loss Function}
The loss function used in this paper is categorical cross-entropy. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and $C$ is the number of training examples and number of class respectively. The categorical cross-entropy loss is presented in the Equation \ref{eqn:weightlossfunction}.
\begin{equation}
	\label{eqn:weightlossfunction}
	L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)
\end{equation}

where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$. Since the data set face the imbalanced problem then class weight for the loss is applied. In this research, both of the original weight and a new weight formula is implementation. Originally, the weight is calculated by taking the inverse of percentage that each class accounts for. The new weight formula is described in the Equation \ref{eqn:weightformula} and \ref{eqn:vector-inverse-percent}. \add{This weight formula is the original weight multiplies with the inverse of number of class in the data set which make the training more balanced. It is inspired by the “balanced” heuristic proposed by Gary King et al\mbox{\cite{WV006-01}}}

\begin{equation}
	\label{eqn:weightformula}
	W = N \odot D
\end{equation}

\begin{equation}
	\label{eqn:vector-inverse-percent}
	D = \begin{bmatrix}
		\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
	\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
		\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
	\end{bmatrix}
\end{equation}

where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.
